The zoon R package for reproducible and shareable species distribution modelling

### 2017-01-17 ms.Rmd
Change text and legends to more accurately reflect feng analysis. * No raw data in PrintMap (for clarity I assume). *MESS masking only in interactive map. * We do not only us USA data. * Clarify what is thresholded.

This workflow plots a static map of the predicted distribution, and the underlying data.
This map is shown in Figure 2A and corresponds to figure 3 in @Feng2015.
The resulting workflow contains all the code required to re-run the workflow, the input data and the results of executing each module.
The object `FengPapes` could therefore be saved as a binary file and shared as a reproducible representation of this research.

@@

```{r feng_papes_plots, cache = FALSE, echo = FALSE, out.width = "450px", fig.cap = "Outputs of the workflow objects `FengPapes' and `FengPapesUpdate'. A) Map of the presence data (red), background data (black) and the MaxEnt relative probability of occurrence generated by the `PrintMap' module in the workflow `FengPapes' which encodes a whole published analysis. White areas are masked due to being in the sea or outside the MESS mask. B) A response curve produced by the `ResponseCurve' module for the first covariate, bio1 in the workflow `FengPapesUpdate', which modifies the original analysis workflow. C) A screenshot of the interactive map produced by the `InteractiveMap' modules in the workflow `FengPapesUpdate', displaying raw occurrence data and predicted distribution over a global map, allowing users to interactively explore their results. Any SDM analysis distributed as a zoon workflow can be easily be explored and scrutinized by modifying its output modules using the function `ChangeWorkflow'."}
knitr::include_graphics("figs/combinefengupdate-1.png")
```

>>>>

This workflow plots a static map of the predicted distribution.
This map is shown in Figure 2A and corresponds to figure 3 in @Feng2015.
The resulting workflow contains all the code required to re-run the workflow, the input data and the results of executing each module.
The object `FengPapes` could therefore be saved as a binary file and shared as a reproducible representation of this research.

@@

```{r feng_papes_plots, cache = FALSE, echo = FALSE, out.width = "450px", fig.cap = "Outputs of the workflow objects `FengPapes' and `FengPapesUpdate'. A) Map of the MaxEnt predicted distribution thresholded at 5% by the `PrintMap' module in the workflow `FengPapes' which encodes a whole published analysis. B) A response curve produced by the `ResponseCurve' module for the first covariate, bio1 in the workflow `FengPapesUpdate', which modifies the original analysis workflow. C) A screenshot of the interactive map produced by the `InteractiveMap' modules in the workflow `FengPapesUpdate', displaying raw occurrence data and predicted distribution over a global map, allowing users to interactively explore their results. White areas are masked due to being in the MESS mask. Any SDM analysis distributed as a zoon workflow can be easily be explored and scrutinized by modifying its output modules using the function `ChangeWorkflow'."}
knitr::include_graphics("figs/combinefengupdate-1.png")
```
